A fast algorithm for computing best response strategies in two-person sequential games

### 2014-07-26 paper.tex
more

\begin{remark}
Equation \eqref{eq:pd_opt} is the form of equation (2) in \cite{chambolle2010} if we take $X := \mathbb{R}^n$ and
$Y := \mathbb{R}^m \times \mathbb{R}^p$.
\end{remark}

>>>>

\begin{remark}
Equation \eqref{eq:pd_opt} is in the form of equation (2) in \cite{chambolle2010} if we take $X := \mathbb{R}^n$ and
$Y := \mathbb{R}^m \times \mathbb{R}^p$.
\end{remark}
